Nonlinear Tidal Dissipation in Binary White Dwarfs

### 2019-03-06 proposal/FINESST/Su_FINESST_2019.tex
word
update proposal one last time

\pagestyle{fancy}
\rfoot{Yubo Su}
\rhead{}
\cfoot{\thepage/\pageref{LastPage}}

@@

This project is extremely relevant to the NASA Astrophysics Division, both in
terms of supporting the division's objectives and enhancing the science output
from NASA missions. My work directly relates to (i) the interactions of
particles under the extreme conditions found in astrophysical situations, (ii)
how complex systems create and shape the structure and composition of the
universe on all scales, and (iii) the development of new techniques that can be
applied to future major missions.

Towards (i), my work will improve understanding of possible energetic phenomena
that can occur in compact object binaries. Towards (ii), my results concerning
angular momentum transfer via IGW breaking will be applicable to astrophysical
systems beyond WD binaries, for instance in massive stars\cite{l_trans_rev}.
Towards (iii), my work has direct relevance to NASA missions by forecasting
astrophysical transients related to WD binaries. For instance, tidal novae are
theorized to have a similar observational signature to dwarf novae which have
been observed with Chandra and the Hubble Space Telescope, among others.
Additionally, my GW templates will also be important for LISA GW detection
efforts.

>>>>

\pagestyle{fancy}
\rhead{}
\cfoot{\thepage/\pageref{LastPage}}

@@

This project is extremely relevant to the NASA Astrophysics Division, both in
terms of supporting the division's objectives and enhancing the science output
from NASA missions. My work directly relates to NASA objectives: (i) ``the
interactions of particles under the extreme conditions found in astrophysical
situations'', (ii) ``how complex systems create and shape the structure and
composition of the universe on all scales'', and (iii) ``the development of new
techniques that can be applied to future major missions''.

Towards (i), my work will improve understanding of possible energetic phenomena
that can occur in compact object binaries. Towards (ii), my results concerning
angular momentum transfer via IGW breaking will be applicable to astrophysical
systems beyond WD binaries, for instance in massive stars\cite{l_trans_rev}.
Towards (iii), my work has direct relevance to NASA missions by forecasting
astrophysical transients related to WD binaries. For instance, tidal novae are
theorized to have a similar observational signature to dwarf novae which have
been observed with Chandra and the Hubble Space Telescope, among others.
Additionally, my GW templates will be important for LISA GW detection efforts.
